MLPPI Wizard: An Automated Multi-Level Partitioning Tool on Analytical Workloads

### 2017-02-23 mlppi-comsis17/cover-letter.tex
comsis version of MLPPI

\opening{Dear Editor-in-Chief:}

\noindent This letter to be submitted to IEICE Transactions on Information and Systems 
presents the following contributions. No version of this letter was submitted earlier.

@@

\item We provide empirical evidence that measuring program time 
can be seriously affected by extant system daemons.

\item We propose a novel timing protocol, called {\em SEDONA} (Selective Elimination through Detection of infrequent, lOng-ruNning dAemons), 
that identifies infrequent, long-running daemons that impact the timing results for that program.

\item We evaluate the performance of the protocol with rigorous experiments, starting from a simple program in pure-computation mode 
to a popular industrial benchmark suite.

\item Experimental results show a strong support for the effectiveness of our SEDONA timing protocol. 
\end{itemize}

>>>>

\opening{Dear Prof. Vladimir Kurbalija (or Editor-in-Chief):}

\noindent An earlier version of this submission was published in Proceedings of the 21st ACM \hbox{International} Conference on Information and Knowledge Management (CIKM). 
This version to be submitted to Computer Science and Information Systems includes the following substantial extensions.

@@

\item Expanded Algorithms: we expand the description of the pre-processing, initial and optimized phase algorithms shortened in the earlier version. Furthermore, this submission contains three additional algorithms as follows:

\item splitting overlapping ranges in Algorithm~2 on page~4,
\item checking the allowed field count limit on the split ranges on in Section 2.1.4 on page~5,
\item computing scan cost in Algorithm~3 on page~6, and
\item computing query cost in Algorithm~5 on page~7.

\end{itemize}

\item Complexity Analysis: we conduct the asymptotic running time analysis on each phase in Section 3 on page 8.

\item Experiments: we provide additional runtime statistics on the workloads used in the experiments in Table 1 on page 10. 
In addition, we compare the quality of a human expert's recommendation with that of our wizard in Figure 5 on page 10.

\item Expanded Literature Review: the related work section on page~9 elaborates in detail on the similarities and differences between our wizard and existing tools.

\end{itemize}
